Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-15 1047_sp.tex
add

\section{More Results on Dataset \cite{ncwebsite}}
In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}. As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{3mm}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_cbm3d.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_wnnm.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_mlp.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\vspace{-2mm}
\caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig1}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{3mm}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_circuit.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_circuit.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_circuit.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_circuit.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_circuit.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_circuit.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_circuit.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_circuit.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\vspace{-2mm}
\caption{Denoised images of the real noisy image ``Circuit" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig2}
\end{figure}

@@

%------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------
\clearpage
\section{More Results on The 15 Cropped Images in \cite{crosschannel2016}}
In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}. As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

>>>>

\section{More Results on Real Noisy Images in \cite{ncwebsite}}
In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}. The real noisy images in this dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods. As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{2mm}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_cbm3d.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_wnnm.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_mlp.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\vspace{-2mm}
\caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig1}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_circuit.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_circuit.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_circuit.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_circuit.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_circuit.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_circuit.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_circuit.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_circuit.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\vspace{-2mm}
\caption{Denoised images of the real noisy image ``Circuit" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig2}
\end{figure}

@@

%------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------
\section{More Results on the 15 Cropped Images in \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}. As can be seen from Fiures \ref{fig5}-\ref{fig8}, our proposed method achieves better performance than the the competing methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
